---
title: "ESM262-Assignment3-Vela"
author: "Alejandro Vela"
date: "6/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###ESM262 - Assignment 3: Functions and Packages

#### Problem 1 
#### Write a function that summaries fish catches for different locations that takes as input:
##### - A table that has prices for different fish.
##### - A Table that has the number caught for each fish species for each location.
##### - Each Location is in a different column.
##### - Each fish in a different row.
####Function output will be:
##### - Most frequently caught fish in each location.
##### - Total revenue for each location.
##### - Total fisheries revenue sum.
##### - If user requests it graph of revenue by location and total revenue (as text)

#### Generating Random Tables for Function 1:
```{r}

# generating the price table 
prices_glob<-c(seq(4,20))
dollar_price_per_unit<-sample(prices_glob,4,replace=FALSE)
type_of_fish<-c("Tuna","Catfish","Salmon","Swordfish")
price_table<-data.frame(type_of_fish,dollar_price_per_unit)

# generating location and sales table
names_of_fish<-c("Tuna","Catfish","Salmon","Swordfish")
type_of_fish<-sample(names_of_fish,4,replace=FALSE)
quantity<-c(seq(50,100))
Los_Angeles<-sample(quantity,4)
Santa_Barbara<-sample(quantity,4)
Ventura<-sample(quantity,4)
San_Francisco<-sample(quantity,4)
number_table<-data.frame(type_of_fish,Los_Angeles, Santa_Barbara, Ventura, San_Francisco)



```
#### Example of ramdon generated table for location wise sales figures: 

```{r}
number_table
```
#### Example of random generated table for fish and price per unit:
```{r}
price_table
```

#### Installing and loading the created package
```{r}
#Package is unzipped in folder "FishPackage"
install.packages("FishPackage",repos=NULL,type="source")

#Loading the library
library(fish)

```

#### Help for both functions
```{r}
#getting help for the function summarize
help(summarize)

#### getting help on the function growth_estimate
help(growth_estimator)
```

#### We test the function summarize below:

```{r}
#Testing the function with the random generated table above
fish:::summarize(price_table,number_table,1)
```

#### Problem 2
#### The relationship between specific growth rate (G) and temperature in °C (T) estimated by a third order polynomial (G=a+bT+cT**2+d*T**3 ), where a,b,c,d and are parameters (input of the function).


##### We test the function growth_estimator below:
```{r}
values<-fish:::growth_estimator(a=-0.4970,b=0.1656,c=0.08588,d=-0.004266,temp=10)
print("the values of growth are :")
print(values)
```
